Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2019-07-18 paper/galsize_paper.tex
Updated figure 6 to include jackknife errors around the purple curves

%--------------------------------------------------------------------------
\subsection{Testing the Impact of Satellite Mass Loss}
\label{subsec:mstar_stripping}
%--------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=11cm]{FIGS/alt_model_wp_ratios.pdf}
\caption{
{\bf The subdominant role of tidal stripping.}
In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}. The solid green curves show the prediction of a model where $\rhalf$ is statistically set by $\mstar,$ in the complete absence of satellite mass loss. Such a model predicts zero $\rhalf-$dependence to galaxy clustering, in gross tension with observations. The solid purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}. This produces satellites that are smaller than centrals, but the effect is too mild to correctly capture the observed clustering. Evidently, satellite-specific mass stripping plays a sub-dominant role in setting the relative size of centrals and satellites.
}
\label{fig:mstarmodelclustering}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

Figure~\ref{fig:mstarmodelclustering} is analogous to Figure \ref{fig:clustering_ratio_upshot}, but instead compares observed clustering ratios to those predicted by models
in which galaxy size is controlled by $\mstar$ (\S\ref{subsubsec:strippingmodel}). Green solid lines show predictions of the $\mstar$-based model that does not account for mass loss due to tides. In this model, $\rhalf$ follows a purely random log-normal distribution, with the median relation $\median{\rhalf}{\mstar}$ directly matched to the observed relation by construction.  This model thus predicts no dependence of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other variable. The figure shows that this model clearly is at odds with the significant dependence of clustering on size exhibited by SDSS galaxies. Error bars are not shown for this model but they are comparable to the errors shown on the purple curves calculated through same jackknife estimation method used in Figure~\ref{fig:clustering_ratio_upshot}.

>>>>

%--------------------------------------------------------------------------
\subsection{Testing the Impact of Satellite Mass Loss}
\label{subsec:mstar_stripping}
%--------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=11cm]{FIGS/alt_model_wp_ratios.pdf}
\caption{
{\bf The subdominant role of tidal stripping.}
In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}. The green curves show the prediction of a model where $\rhalf$ is statistically set by $\mstar,$ in the complete absence of satellite mass loss. Such a model predicts zero $\rhalf-$dependence to galaxy clustering, in gross tension with observations. The purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}. This produces satellites that are smaller than centrals, but the effect is too mild to correctly capture the observed clustering. Evidently, satellite-specific mass stripping plays a sub-dominant role in setting the relative size of centrals and satellites.
}
\label{fig:mstarmodelclustering}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

Figure~\ref{fig:mstarmodelclustering} is analogous to Figure \ref{fig:clustering_ratio_upshot}, but instead compares observed clustering ratios to those predicted by models
in which galaxy size is controlled by $\mstar$ (\S\ref{subsubsec:strippingmodel}). Green curves show predictions of the $\mstar$-based model that does not account for mass loss due to tides. In this model, $\rhalf$ follows a purely random log-normal distribution, with the median relation $\median{\rhalf}{\mstar}$ directly matched to the observed relation by construction.  This model thus predicts no dependence of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other variable. The figure shows that this model clearly is at odds with the significant dependence of clustering on size exhibited by SDSS galaxies.
